DOM Review Summary

### 2024-03-16 Analysis/ReviewSummary/ReviewSummary.qmd
Study area size
Plot for study area size in kilometres

>>>>

Consistent with authorship trends, a majority of articles conducted studies in the United States.

::: panel-tabset
## Country

```{r Species_Country}
#| echo: false

species_clean |> 
  select(ID_clean, Country) |>
  separate_rows(Country, sep = ", ") |> 
  distinct() |>
  summarise(Articles = n(), .by = Country) |>
  arrange(-Articles) |>
  reactable(defaultPageSize = 8)
```

## Continent

```{r Species_Continent}
#| echo: false

species_clean |> 
  select(ID_clean, Continent) |>
  distinct() |>
  summarise(Articles = n(), .by = Continent) |>
  arrange(-Articles) |>
  reactable(defaultPageSize = 8)
```

## Realm

```{r Species_Realm}
#| echo: false

species_clean |> 
  select(ID_clean, Realm) |>
  distinct() |>
  summarise(Articles = n(), .by = Realm) |>
  arrange(-Articles) |>
  reactable(defaultPageSize = 8)

```
:::

```{r Species_locations}

## Study area size

The size of the study area in square kilometres follows a log-normal distribution, with studies ranging from less than one to over one million square kilometres.

```{r Species_sizeKM}
#| echo: false

species_clean |> 
  select(ID_clean, Size_km) |>
  distinct() |>
  mutate(Size_km = case_when(Size_km == "<1" ~ "0-1",
                             Size_km == "1000-9999" ~ "1000-10000",
                             .default = Size_km)) |>
  summarise(Articles = n(), .by = Size_km) |>
  arrange(Size_km) |>
  mutate(Size_km = fct_inorder(Size_km)) |> 
  filter(!Size_km %in% c("Not specified", "Unspecified")) |>

  ggplot() +
  geom_col(aes(x = Size_km, y = Articles), fill = "darkslategrey") +
  labs(title = "Study area size",
       x = "Study area in square kilometres", 
       y = "Number of articles") +
  theme(axis.text.x = element_text(angle = 60, vjust = 0.5))
